PANNEURO_analysis

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
Changed data file for analyses to combined dataset with baseline and CFS data.

## Read in data
```{r read in data}
dat.raw <- readRDS(file = paste0(data_path, "/four_cohorts.rds")) #NEEDS CHANGING
dim(dat.raw)
colnames(dat.raw)
```

>>>>

## Read in data
```{r read in data}
dat.raw <- readRDS(file = paste0(data_path, "/baseline_and_cfs_wave6.rds")) #NEEDS CHANGING
dim(dat.raw)
colnames(dat.raw)
```
